% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Li Yangcheng}

\basicInfo{
  \email{herkoalabear@hotmail.com} \textperiodcentered\ 
  \phone{(+86) 18001560090}}

\section{Education}
\datedsubsection{\textbf{Shanghai Jiao Tong University (SJTU)}, Shanghai, China}{2020 -- Present}
\textit{Master student} in Computer Science and technology (CS), expected June 2023
\datedsubsection{\textbf{Central South University (CSU)}, Changsha, China}{2016 -- 2020}
\textit{B.Eng.} in Computer Science and technology (CS)

\section{Paper}
Synpose: A Large-Scale and Densely Annotated Synthetic Dataset for Human Pose Estimationin Classroom Zefang Yu,
\textbf{Yangcheng Li}, Yicheng Liu, Ting Liu, Yuzhuo Fu. \textbf{ICASSP} 2022
\begin{itemize}
  \item We open source SynPose, a large, densely labeled synthetic dataset specifically designed for crowded human pose estimation in classroom and meeting scenarios.
  \item We propose a novel CTGAN to bridge the domain gap.
  \item Details about this dataset can be founded at: {\underline{\url{https://yuzefang96.github.io/SynPose/}}}.
\end{itemize}

\section{Experience}
\datedsubsection{Participate in open source community project: {\underline{\href{https://github.com/open-mmlab/mmaction2}{mmAction2}}}}{May. 2022}
\begin{itemize}
  \item Participate in the discussion of relevant issues: {\underline{\href{https://github.com/open-mmlab/mmaction2/issues/1624}{\#1624}}}, {\underline{\href{https://github.com/open-mmlab/mmaction2/issues/1628}{\#1628}}}, {\underline{\href{https://github.com/open-mmlab/mmaction2/issues/1640}{\#1640}}}, {\underline{\href{https://github.com/open-mmlab/mmaction2/issues/1662}{\#1662}}}
  \item Contribute to the pull requests: {\underline{\href{https://github.com/open-mmlab/mmaction2/pull/1622}{\#1622}}}, {\underline{\href{https://github.com/open-mmlab/mmaction2/pull/1627}{\#1627}}}, {\underline{\href{https://github.com/open-mmlab/mmaction2/pull/1630}{\#1630}}}
\end{itemize}

\datedsubsection{\textbf{xxx Projects}}{Jan. 2015 -- Present}
\role{C, Python, Django, Linux}{Individual Projects, collaborated with xxx}
Brief introduction: xxx
\begin{itemize}
  \item Implemented xxx feature
  \item Optimized xxx 5\%
  \item xxx
\end{itemize}

\datedsubsection{\textbf{\LaTeX\ résumé template}}{May. 2015 -- Present}
\role{\LaTeX, Maintainer}{Individual Projects}
An elegant \LaTeX\ résumé template, https://github.com/billryan/resume
\begin{itemize}
  \item Easy to be further customized or extended
  \item Full support for unicode characters (e.g. CJK) with \XeLaTeX\
  \item FontAwesome 4.5.0 support
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C == Python > C++ > Java
  \item Platform: Linux
  \item Development: Web, xxx
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
\datedline{Other awards}{2015}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: http://your.blog.me
  \item GitHub: https://github.com/username
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
